---
title: "Data_curation"
author: "Anonymous for peer-review"
date: "latest update: `r format(Sys.time(), '%d %B %Y')`"
output: rmdformats::readthedown
editor_options: 
  chunk_output_type: inline
---


```{r setup, include = FALSE}
# knitr setting
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE, 
  tidy = TRUE,
  cache = TRUE
)
```


# **Load packages and data**

## *Load packages* 

```{r}
pacman::p_load(tidyverse,
               maps,
               ape,
               patchwork,
               ggtree, # devtools::install_github("YuLab-SMU/ggtree")
               ggtreeExtra, # devtools::install_github("xiangpin/ggtreeExtra")
               ggnewscale, # this package is necessary for building trees
               here,
               ggspatial) 

```

## *Load data and phylogenetic tree*

This tree is the consensus tree from Pyron and Jetz (2018)

```{r}
d.raw<-read_csv("data/Raw_data.csv")

tree<-read.tree("data/amph_shl_new_Consensus_7238.tre") # Load tree
```


# **Harmonise taxonomy**

`15 species` are not included in the tree of Pyron and Jetz (2018): 
- *Amazophrynella javierbustamantei*
- *Aquiloeurycea cafetalera*
- *Chiasmocleis royi*
- *Craugastor metriosistus*         
- *Dendropsophus kamagarini*
- *Gastrotheca lojana*
- *Microkayla quimsacruzis*
- *Pristimantis macrummendozai*
- *Pseudacris hypochondriaca* 
- *Rhinella horribilis*
- *Scinax tsachila*
- *Trachycephalus typhonius*
- *Zhangixalus moltrechti*
- *Zhangixalus prasinatus*
- *Zhangixalus taipeianus*
Those species were not removed from the curated data.

`9 species` were not described at the species level: 
- *Ameerega sp.*
- *Aplastodiscus sp.*
- *Boana sp.*
- *Crossodactylus sp.*
- *Engystomops sp.*
- *Noblella sp.*
- *Pristimantis sp.* 
- *Psychrophrynella sp.1*
- *Psychrophrynella_sp.2*
Those species were removed from the curated data. 

and `35` species names were up to date with amphibiaweb.org, but did not match the phylogeny of Jetz and Pyron (2018). 
Taxonomic names were found, and we replaced species names to match the phylogeny of Jetz and Pyron (see below)


```{r}

d.treecheck<-select(d.raw, order, family, species) # Only select relevant variables
d.treecheck$species <- gsub(" ", "_", d.treecheck$species) # Add underscore between species names

'%!in%' <- function(x,y)!('%in%'(x,y)) # Function opposite of %in%

d.not_in_tree<-d.treecheck[d.treecheck$species %!in% tree$tip.label, ] # Find species not matching the tree

species_tree<-as.data.frame(tree$tip.label) # To check species in the tree
species<-as.data.frame(d.raw$species) # To check species in the raw data

# Replace species names not matching the tree
d.raw$species[d.raw$species =="Agalychnis dacnicolor"] <- "Pachymedusa dacnicolor"
d.raw$species[d.raw$species =="Anaxyrus caronus"] <- "Anaxyrus canorus"
d.raw$species[d.raw$species =="Boana albomargina"] <- "Hypsiboas albomarginatus"
d.raw$species[d.raw$species =="Boana albopunctata"] <- "Hypsiboas albopunctatus"
d.raw$species[d.raw$species =="Boana almendarizae"] <- "Hypsiboas almendarizae"
d.raw$species[d.raw$species =="Boana boans"] <- "Hypsiboas boans"
d.raw$species[d.raw$species =="Boana cinerascens"] <- "Hypsiboas cinerascens"
d.raw$species[d.raw$species =="Boana crepitans"] <- "Hypsiboas crepitans"
d.raw$species[d.raw$species =="Boana curupi"] <- "Hypsiboas curupi"
d.raw$species[d.raw$species =="Boana faber"] <- "Hypsiboas faber"
d.raw$species[d.raw$species =="Boana fasciata"] <- "Hypsiboas fasciatus"
d.raw$species[d.raw$species =="Boana geographica"] <- "Hypsiboas geographicus"
d.raw$species[d.raw$species =="Boana lanciformis"] <- "Hypsiboas lanciformis"
d.raw$species[d.raw$species =="Boana pardalis"] <- "Hypsiboas pardalis"
d.raw$species[d.raw$species =="Boana pellucens"] <- "Hypsiboas pellucens"
d.raw$species[d.raw$species =="Boana pulchella"] <- "Hypsiboas pulchellus"
d.raw$species[d.raw$species =="Boana punctata"] <- "Hypsiboas punctatus"
d.raw$species[d.raw$species =="Boana raniceps"] <- "Hypsiboas raniceps"
d.raw$species[d.raw$species =="Boana rosenbergi"] <- "Hypsiboas rosenbergi"
d.raw$species[d.raw$species =="Boana rufitela"] <- "Hypsiboas rutifelus"
d.raw$species[d.raw$species =="Boana semilineata"] <- "Hypsiboas semilineatus"
d.raw$species[d.raw$species =="Chalcorana labialis"] <- "Hylarana labialis"
d.raw$species[d.raw$species =="Chiasmocleis bassleri"] <- "Syncope bassleri"
d.raw$species[d.raw$species =="Hyalinobatrachium fleischmann"] <- "Hyalinobatrachium fleischmanni"
d.raw$species[d.raw$species =="Hyla crucifer"] <- "Pseudacris crucifer"
d.raw$species[d.raw$species =="Hyloxalus jacobuspetersi"] <- "Colostethus jacobuspetersi"
d.raw$species[d.raw$species =="Hynobius fucus"] <- "Hynobius fuca"
d.raw$species[d.raw$species =="Lithobates sphenocephalus"] <- "Rana sphenocephala"
d.raw$species[d.raw$species =="Neobatrachus sudellae"] <- "Neobatrachus sudelli"
d.raw$species[d.raw$species =="Nidirana adenopleura"] <- "Babina adenopleura"
d.raw$species[d.raw$species =="Phrynoglossus laevis"] <- "Occidozyga laevis"
d.raw$species[d.raw$species =="Physalaemus nattereri"] <- "Eupemphix nattereri"
d.raw$species[d.raw$species =="Pseudis platentis"] <- "Pseudis platensis"
d.raw$species[d.raw$species =="Rana perezi"] <- "Pelophylax perezi"
d.raw$species[d.raw$species =="Scinax elaeochrous"] <- "Scinax elaeochroa"

```

# **Correct mistakes** 

Family names were incorrect for some species.
```{r}
d.raw %>%
     group_by(species) %>%
     summarise(family  = unique(family)) %>%
     filter(n()>1)

d.raw$family[d.raw$species =="Eleutherodactylus coqui"] <- "Eleutherodactylidae"
d.raw$family[d.raw$species =="Mixophyes fasciolatus"] <- "Myobatrachidae"
d.raw$family[d.raw$species =="Pelodytes ibericus"] <- "Pelodytidae"
d.raw$family[d.raw$species =="Pelodytes punctatus"] <- "Pelodytidae"
d.raw$family[d.raw$species =="Pelophylax perezi"] <- "Ranidae"
```

# **Descriptive statistics for the raw data**

```{r}
n_distinct(d.raw$es_ID) # 3095 effect sizes
n_distinct(d.raw$ref) # 213 studies
n_distinct(d.raw$species) # 616 species
n_distinct(d.raw$population_ID) # 1166 populations 
n_distinct(d.raw$cohort_ID) # 2883 cohorts
n_distinct(d.raw$family) # 37 families

d.raw %>% group_by(ref) %>% 
          summarise(n_sp = n_distinct(species),
                    n_pop = n_distinct(population_ID),
                    n_es = n_distinct(es_ID)) %>% 
          ungroup() %>% 
          summarise(`Number of species per study` = mean(n_sp),
                    `SD species per study` = sd(n_sp),
                    `Minimum number of species per study` = min(n_sp),
                    `Maximum number of species per study` = max(n_sp),
                    
                    `Number of populations per study` = mean(n_pop),
                    `SD populations per study` = sd(n_pop),
                    `Minimum number of populations per study` = min(n_pop),
                    `Maximum number of populations per study` = max(n_pop),
                    
                    `Number of estimates per study` = mean(n_es),
                    `SD estimates per study` = sd(n_es),
                    `Minimum number of estimates per study` = min(n_es),
                    `Maximum number of estimates per study` = max(n_es))
# 4.97 (+/- 10.2) species per study on average (range: 1-75)
# 5.93 (+/- 10.7) populations per study on average (range: 1-75)
# 14.53 estimates (+/- 27.3) estimates per study on average (range: 1-230)

d.raw %>% group_by(species) %>% 
          summarise(n_pop = n_distinct(population_ID),
                    n_es = n_distinct(es_ID)) %>% 
          ungroup() %>% 
          summarise(`Number of populations per species` = mean(n_pop),
                    `SD populations per species` = sd(n_pop),
                    `Minimum number of populations per species` = min(n_pop),
                    `Maximum number of populations per species` = max(n_pop),
                    
                    `Number of estimates per species` = mean(n_es),
                    `SD estimates per species` = sd(n_es),
                    `Minimum number of estimates per species` = min(n_es),
                    `Maximum number of estimates per species` = max(n_es))
# 1.93 (+/- 2.35) populations per species on average (range: 1-26)
# 5.02 (+/- 12.6) estimates per species on average (range : 1-163)

d.raw %>% group_by(language) %>% 
          summarise(n_st = n_distinct(ref),
                    n_sp = n_distinct(species_ID),
                    n_pop = n_distinct(population_ID),
                    n_es = n_distinct(es_ID)) 
# Number of studies, species, populations and estimates for by publication language


d.raw %>% group_by(name) %>% 
          summarise(n_st = n_distinct(ref),
                    n_es = n_distinct(es_ID)) %>% 
          mutate(percent_st = (n_st/214)*100,
                 percent_es = (n_es/3095)*100) # Percentage of studies and effect sizes extracted by each author

n_distinct(d.raw$es_ID[is.na(d.raw$error_UTL)==TRUE]) # Number of estimates missing measures of dispersion
```

# **Data curation**

## *Remove species not described at the species level*
```{r}
d.curated <- filter(d.raw, !str_detect(d.raw$species, "\\.")) 
```

## *Remove extinct species*

Remove one extinct species: *Taudactylus diurnus* (2 estimates)
```{r}
d.curated <- filter(d.curated, IUCN_status!="EX") 
```

## *Remove animals exposed to hormones or chemicals* 

```{r}
d.curated <- filter(d.curated, is.na(concentration_chemical_hormone)==TRUE|concentration_chemical_hormone==0)
```

## *Remove data with procedural concerns* 

```{r}
d.curated <- filter(d.curated, is.na(flag)==TRUE)
```

## *Export data*

```{r}
write_csv(d.curated, file=here("data/Curated_data.csv"))
```


# **Descriptive statistics for the curated data**

```{r}

n_distinct(d.curated$es_ID) # 2888 effect sizes
n_distinct(d.curated$ref) # 197 studies
n_distinct(d.curated$species) # 587 species
n_distinct(d.curated$population_ID) # 1109 populations 
n_distinct(d.curated$cohort_ID) # 2680 cohorts
n_distinct(d.curated$family) # 36 families

d.curated %>% group_by(ref) %>% 
          summarise(n_sp = n_distinct(species),
                    n_pop = n_distinct(population_ID),
                    n_es = n_distinct(es_ID)) %>% 
          ungroup() %>% 
          summarise(`Number of species per study` = mean(n_sp),
                    `SD species per study` = sd(n_sp),
                    `Minimum number of species per study` = min(n_sp),
                    `Maximum number of species per study` = max(n_sp),
                    
                    `Number of populations per study` = mean(n_pop),
                    `SD populations per study` = sd(n_pop),
                    `Minimum number of populations per study` = min(n_pop),
                    `Maximum number of populations per study` = max(n_pop),
                    
                    `Number of estimates per study` = mean(n_es),
                    `SD estimates per study` = sd(n_es),
                    `Minimum number of estimates per study` = min(n_es),
                    `Maximum number of estimates per study` = max(n_es))
# 5.09 (+/- 10.3) species per study on average (range: 1-74)
# 6.12 (+/- 10.9) populations per study on average (range: 1-74)
# 14.66 estimates (+/- 28.0) estimates per study on average (range: 1-230)

d.curated %>% group_by(species) %>% 
          summarise(n_pop = n_distinct(population_ID),
                    n_es = n_distinct(es_ID),
                    n_acc = n_distinct(acclimation_temp)) %>% 
          ungroup() %>% 
          summarise(`Number of populations per species` = mean(n_pop),
                    `SD populations per species` = sd(n_pop),
                    `Minimum number of populations per species` = min(n_pop),
                    `Maximum number of populations per species` = max(n_pop),
                    
                    `Number of estimates per species` = mean(n_es),
                    `SD estimates per species` = sd(n_es),
                    `Minimum number of estimates per species` = min(n_es),
                    `Maximum number of estimates per species` = max(n_es))
# 1.93 (+/- 2.37) populations per species on average (range: 1-26)
# 4.92 (+/- 12.08) estimates per species on average (range : 1-146)

d.curated %>% group_by(language) %>% 
          summarise(n_st = n_distinct(study_ID),
                    n_sp = n_distinct(species_ID),
                    n_pop = n_distinct(population_ID),
                    n_es = n_distinct(es_ID)) 
# Number of studies, species, populations and estimates for by publication language

n_distinct(d.curated$es_ID[is.na(d.curated$error_UTL)==TRUE]) # Number of estimates missing measures of dispersion
```

# **Package versions**
```{r}
sessionInfo()
```

