---
title: "Figures_data_descriptor"
author: "Anonymous for peer-review"
date: "latest update: `r format(Sys.time(), '%d %B %Y')`"
output: rmdformats::readthedown
editor_options: 
  chunk_output_type: console
---


```{r setup, include = FALSE}
# knitr setting
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE, 
  tidy = TRUE,
  cache = TRUE
)
```

# **Load packages and data**

## *Load packages*

```{r}
pacman::p_load(tidyverse,
               maps,
               ape,
               patchwork,
               ggtree, # devtools::install_github("YuLab-SMU/ggtree")
               ggtreeExtra, # devtools::install_github("xiangpin/ggtreeExtra")
               ggnewscale, # this package is necessary for building trees
               here,
               ggspatial,
               viridis,
               RColorBrewer) 
```


## *Load data and tree*

```{r}
d.raw<-read_csv("data/Raw_data.csv") # Import data

tree<-read.tree("data/amph_shl_new_Consensus_7238.tre") # Import tree
```

# **Match species names to the tree** 

```{r}
# Rename species to match the tree
d.raw$species[d.raw$species =="Agalychnis dacnicolor"] <- "Pachymedusa dacnicolor" 
d.raw$species[d.raw$species =="Anaxyrus caronus"] <- "Anaxyrus canorus"
d.raw$species[d.raw$species =="Boana albomargina"] <- "Hypsiboas albomarginatus"
d.raw$species[d.raw$species =="Boana albopunctata"] <- "Hypsiboas albopunctatus"
d.raw$species[d.raw$species =="Boana almendarizae"] <- "Hypsiboas almendarizae"
d.raw$species[d.raw$species =="Boana boans"] <- "Hypsiboas boans"
d.raw$species[d.raw$species =="Boana cinerascens"] <- "Hypsiboas cinerascens"
d.raw$species[d.raw$species =="Boana crepitans"] <- "Hypsiboas crepitans"
d.raw$species[d.raw$species =="Boana curupi"] <- "Hypsiboas curupi"
d.raw$species[d.raw$species =="Boana faber"] <- "Hypsiboas faber"
d.raw$species[d.raw$species =="Boana fasciata"] <- "Hypsiboas fasciatus"
d.raw$species[d.raw$species =="Boana geographica"] <- "Hypsiboas geographicus"
d.raw$species[d.raw$species =="Boana lanciformis"] <- "Hypsiboas lanciformis"
d.raw$species[d.raw$species =="Boana pardalis"] <- "Hypsiboas pardalis"
d.raw$species[d.raw$species =="Boana pellucens"] <- "Hypsiboas pellucens"
d.raw$species[d.raw$species =="Boana pulchella"] <- "Hypsiboas pulchellus"
d.raw$species[d.raw$species =="Boana punctata"] <- "Hypsiboas punctatus"
d.raw$species[d.raw$species =="Boana raniceps"] <- "Hypsiboas raniceps"
d.raw$species[d.raw$species =="Boana rosenbergi"] <- "Hypsiboas rosenbergi"
d.raw$species[d.raw$species =="Boana rufitela"] <- "Hypsiboas rutifelus"
d.raw$species[d.raw$species =="Boana semilineata"] <- "Hypsiboas semilineatus"
d.raw$species[d.raw$species =="Chalcorana labialis"] <- "Hylarana labialis"
d.raw$species[d.raw$species =="Chiasmocleis bassleri"] <- "Syncope bassleri"
d.raw$species[d.raw$species =="Hyalinobatrachium fleischmann"] <- "Hyalinobatrachium fleischmanni"
d.raw$species[d.raw$species =="Hyla crucifer"] <- "Pseudacris crucifer"
d.raw$species[d.raw$species =="Hyloxalus jacobuspetersi"] <- "Colostethus jacobuspetersi"
d.raw$species[d.raw$species =="Hynobius fucus"] <- "Hynobius fuca"
d.raw$species[d.raw$species =="Lithobates sphenocephalus"] <- "Rana sphenocephala"
d.raw$species[d.raw$species =="Neobatrachus sudellae"] <- "Neobatrachus sudelli"
d.raw$species[d.raw$species =="Nidirana adenopleura"] <- "Babina adenopleura"
d.raw$species[d.raw$species =="Phrynoglossus laevis"] <- "Occidozyga laevis"
d.raw$species[d.raw$species =="Physalaemus nattereri"] <- "Eupemphix nattereri"
d.raw$species[d.raw$species =="Pseudis platentis"] <- "Pseudis platensis"
d.raw$species[d.raw$species =="Rana perezi"] <- "Pelophylax perezi"
d.raw$species[d.raw$species =="Scinax elaeochrous"] <- "Scinax elaeochroa"
```

Note that each figure underwent cosmetic changes in Microsoft PowerPoint. 

# **Figure 2**

## *Figure 2A* 

Adult phylogenetic tree 

```{r}
d.adult<-filter(d.raw, life_stage_tested=="adults") # Only keep data for adults
d.tree.adult<-select(d.adult, order, family, species, acclimation_temp, mean_UTL) # Only select relevant variables
d.tree.adult$species <- gsub(" ", "_", d.tree.adult$species) # Add underscore between species names


d.tree.adult<-d.tree.adult[d.tree.adult$species %in% tree$tip.label, ] # Remove all species not matching the tree

pruned_tree.adult<-drop.tip(tree, tree$tip.label[-match(d.tree.adult$species, tree$tip.label)]) # Pruned tree that only contains species in the data 

d.tree.adult<-mutate(d.tree.adult, tip.label= species) # create a column "tip.label" to match the data to the tree

d.tree.onesp.adult<-group_by(d.tree.adult, tip.label) %>%  # Calculate the mean heat tolerance and number of effect sizes per species
                    summarise(mean_UTL = mean(mean_UTL),
                              n_es = n(),
                              log_n_es=log2(n_es+1)) # Log + 1 for the plot

d.tree.taxo.adult<-select(d.tree.adult, tip.label, order, family) # Only select relevant variables
d.tree.taxo.adult<-distinct(d.tree.taxo.adult) # Remove duplicate species 
d.tree.onesp.adult<-left_join(d.tree.onesp.adult, d.tree.taxo.adult, by="tip.label") # Join the data to the calculated stats for each species

# Plot the tree
p.adult<-ggtree(pruned_tree.adult, 
                layout = "fan", # Circular phylogenetic tree
                lwd = 0.75, 
                aes(colour=order))+
         scale_colour_manual(values=c("#60935D", "#DD9F18"))

p.adult <- p.adult %<+% d.tree.onesp.adult # Match data to the tree

p2.adult <- p.adult + geom_fruit(geom = geom_tile, # Heat map
                                 mapping = aes(fill = mean_UTL), 
                                 width=25, 
                                 offset=0.06) + 
                      scale_fill_viridis(option="plasma", # Colour gradient of the heat map
                                         begin=0.001, 
                                         end=0.95, 
                                         name="Heat tolerance") 
  
p3.adult <- p2.adult + new_scale_fill() + geom_fruit(geom = geom_bar, # Bar plot
                                                     mapping = aes(x = log_n_es,
                                                                   fill = order),  
                                                     stat = "identity", 
                                                     orientation = "y", 
                                                     axis.params = list(axis = "x", # Barplot parameters
                                                                        text.angle = 0, 
                                                                        hjust = 0, 
                                                                        text.size = 2.5,
                                                                        col="transparent"), 
                                                     grid.params = list(alpha = 0.55),
                                                     offset = 0.06, 
                                                     pwidth = 0.25, 
                                                     alpha = 1) + 
                                           scale_fill_manual(values=c("#60935D", "#DD9F18"))+ # Barplot colours
                                           theme(legend.position="bottom", 
                                                 legend.direction ="horizontal")+
                                           guides(colour=F) # Remove duplicated legend

p3.adult 
```

## *Figure 2B*

Juvenile phylogenetic tree. Note that, due to the small number of estimates for juveniles, they were grouped with data for larvae.
```{r}
## Tree with juveniles only 
d.larvae<-filter(d.raw, life_stage_tested=="larvae"|life_stage_tested=="juveniles") # Keep only juveniles or larvae
d.tree.larvae<-select(d.larvae, order, family, species, acclimation_temp, mean_UTL) # Only select relevant variables
d.tree.larvae$species <- gsub(" ", "_", d.tree.larvae$species) # Add underscore between species names


d.tree.larvae<-d.tree.larvae[d.tree.larvae$species %in% tree$tip.label, ] # Remove all species not matching the tree

pruned_tree.larvae<-drop.tip(tree, tree$tip.label[-match(d.tree.larvae$species, tree$tip.label)]) # Pruned tree that only contains species in the data 

d.tree.larvae<-mutate(d.tree.larvae, tip.label= species) # create a column "tip.label" to match the data to the tree
d.tree.onesp.larvae<-group_by(d.tree.larvae, tip.label) %>%  
                     summarise(mean_UTL = mean(mean_UTL),
                               n_es = n(),
                               log_n_es=log2(n_es+1)) # Log +1 for the plot

d.tree.taxo.larvae<-select(d.tree.larvae, tip.label, order, family) # Keep relevant variables
d.tree.taxo.larvae<-distinct(d.tree.taxo.larvae) # Remove duplicate species 
d.tree.onesp.larvae<-left_join(d.tree.onesp.larvae, d.tree.taxo.larvae, by="tip.label") # Join the data to the calculated stats for each species

summary(d.tree.onesp.adult$mean_UTL) # Summary to set the begin and end argument of the heat map
summary(d.tree.onesp.larvae$mean_UTL) 


# Plot the tree
p.larvae<-ggtree(pruned_tree.larvae, 
                 layout = "fan", # Plot a circular tree
                 lwd = 0.75, 
                 aes(colour=order))+
          scale_colour_manual(values=c("#60935D", "#DD9F18"))

p.larvae <- p.larvae %<+% d.tree.onesp.larvae # Match data to the tree
p2.larvae <- p.larvae + geom_fruit(geom = geom_tile, 
                                   mapping = aes(fill = mean_UTL), 
                                   width=25, 
                                   offset=0.06) + 
                        scale_fill_viridis(option="plasma", 
                                           begin=0.00130818, 
                                           end=0.8139635) # Set beginining and end of the colour gradient to match the adult heat map
  
p3.larvae <- p2.larvae + new_scale_fill() + geom_fruit(geom = geom_bar, # Barplot
                                                       mapping = aes(x = log_n_es, 
                                                                     fill = order),  
                                                       stat = "identity", 
                                                       orientation = "y", 
                                                       axis.params = list(axis = "x", # Barplot parameters
                                                                          text.angle = 0, 
                                                                          hjust = 0, 
                                                                          text.size = 2.5,
                                                                          col="transparent"), 
                                                       grid.params = list(alpha = 0.55),
                                                       offset = 0.06, 
                                                       pwidth = 0.25, alpha = 1) + 
                                             scale_fill_manual(values=c("#60935D", "#DD9F18"))+ # Barplot colours
                                             theme(legend.position="none") # Remove legend
p3.larvae 

```

```{r, fig.height=20, fig.width=12}
p3.adult/p3.larvae # Combine adult and larvae plots

#ggsave("output/Fig2_raw.svg", height=20, width=14, dpi=2000, bg="transparent")
```

## Trees with species names

```{r, height=15, width=15}
# Plot the adult tree
p.adult<-ggtree(pruned_tree.adult, 
                layout = "fan", 
                lwd = 0.75, 
                aes(colour=order))+
         scale_colour_manual(values=c("#60935D", "#DD9F18"))

p.adult <- p.adult %<+% d.tree.onesp.adult

p.adult + geom_tiplab(size=2.5)


# Plot the juvenile tree
p.larvae<-ggtree(pruned_tree.larvae, 
                 layout = "fan", 
                 lwd = 0.75, 
                 aes(colour=order))+
          scale_colour_manual(values=c("#60935D", "#DD9F18"))

p.larvae <- p.larvae %<+% d.tree.onesp.larvae

p.larvae + geom_tiplab(size=2.5)

```

# **Figure 3**

```{r}
d.taxonomy<-read_csv("data/amph_shl_new_Classification.csv") # Load amphibian classification from Jetz and Pyron (2018)
d.taxonomy$tip.label<-d.taxonomy$`Scientific Name` # Rename variable to match our dataset
d.taxonomy$order<-d.taxonomy$Taxon # Rename variable to match our dataset
d.taxonomy$tip.label <- gsub(" ", "_", d.taxonomy$tip.label) # Add underscore between species names

d<-d.raw # Copy of raw data
d.tree.all<-select(d, order, family, species, acclimation_temp, mean_UTL, life_stage_tested) # Only select relevant variables
d.tree.all$species <- gsub(" ", "_", d.tree.all$species) # Add underscore between species names


d.tree.all<-mutate(d.tree.all, tip.label= species) # create a column "tip.label" to match the data to the tree

d.tree.onesp.all<-group_by(d.tree.all, tip.label) %>%  # Calculate the mean heat tolerance and number of effect sizes per species
                    summarise(mean_UTL = mean(mean_UTL),
                              n_es = n(),
                              log_n_es=log2(n_es+1)) # Log + 1 for the plot

d.tree.taxo.all<-select(d.tree.all, tip.label, order, family) # Only select relevant variables
d.tree.taxo.all<-distinct(d.tree.taxo.all) # Remove duplicate species 
d.tree.onesp.all<-left_join(d.tree.onesp.all, d.tree.taxo.all, by="tip.label") # Join the data to the calculated stats for each species

species_in_tree<- data.frame(tip.label=tree$tip.label)# Get all species names from Jetz and Pyron (2018)
d.tree.onesp.all<-full_join(d.tree.onesp.all, species_in_tree)
d.tree.onesp.all<- full_join(d.tree.onesp.all, d.taxonomy, by="tip.label")
d.tree.onesp.all <- mutate(d.tree.onesp.all, Order = coalesce(order.x, order.y)) # Combine content columns
d.tree.onesp.all<-filter(d.tree.onesp.all, Order!="Outgroup") # Remove humans


# Plot the tree
p.all<-ggtree(tree, 
                layout = "fan", # Circular phylogenetic tree
                lwd = 0.2,
                aes(colour=Order))+
       scale_colour_manual(values=c("#60935D", "#DD9F18", "#925D83"),
                           na.value="black")

p.all <- p.all %<+% d.tree.onesp.all # Match data to the tree

p2.all <- p.all + geom_fruit(geom = geom_tile, # Heat map
                             mapping = aes(fill = mean_UTL), 
                                           width=25, 
                                           offset=0.06) + 
                  scale_fill_viridis(option="plasma", # Match colour gradient of Fig. 2
                                     begin=0.001, 
                                     end=0.95, 
                                     name="Heat tolerance",
                                     na.value="gray95") +
                  theme(legend.position="bottom", 
                        legend.direction ="horizontal")

p2.all

#ggsave("output/Fig3_raw.svg", height=20, width=20, dpi=3000)

```



# **Figure 4** 

```{r, fig.height=10, fig.width=18}

WorldData <- map_data("world") # Get coordinates
d.map<-d.raw # Copy dataset
d.map$life_stage_tested[d.map$life_stage_tested=="juveniles"]<-"larvae" # Consider juveniles as "larvae"

map <- ggplot(d.map, 
              aes(x = longitude, # Set up plot
                  y = latitude)) + 
       geom_map(data = WorldData, 
                map = WorldData, # Display world data
                aes(x = long,
                    y = lat, 
                    group = group, 
                    map_id = region), 
                fill = "grey95", 
                colour = "#7f7f7f", 
                size = 0.5) + 
       geom_point(data=d.map,  # Display location of species for which we have coordinates
                  aes(fill=order, 
                      col=life_stage_tested, 
                      shape=language), 
                  alpha = 0.6, 
                  size=4, 
                  stroke=1.5) +
       scale_fill_manual(values=c("#60935D", "#DD9F18"), # Set the point inside colour according to orders
                         name="Order", 
                         guide=guide_legend(title.position="top", 
                                            direction="horizontal")) + 
       scale_colour_manual(values=c("black", "#4B0084"),  # Set the point outside colour according to life stages
                           name="Life stage", 
                           labels=c("Adults", "Juveniles"), 
                           guide=guide_legend(title.position="top", 
                                              direction="horizontal")) + 
       scale_shape_manual(values=c(21,22,23,24,25),  # Set the shape of the points according to languages
                          name="Language", 
                          guide=guide_legend(title.position="top", 
                                             direction="horizontal")) + 
       theme_minimal() +  # Simple theme
       theme(text=element_text(size=25),  # Increase font sizes 
             axis.text = element_text(size=20),
             legend.title=element_text(size=20, 
                                       face="italic"),
             legend.text = element_text(size=17),
             legend.position="bottom",
             legend.spacing.x=unit(0.25, "cm"),
             legend.margin=margin(r=25, l=25))+
       scale_x_continuous(breaks=seq(-180, 180, by = 30))+ # Set the limits of the plot
       scale_y_continuous(breaks=seq(-90, 90, by = 30))+
       labs(x = "Longitude", 
            y = "Latitude") +
       annotation_north_arrow(style = north_arrow_nautical(text_size=15, # Add nautical arrow
                                                           fill=c("grey20", "white")), 
                              height=unit(4, "cm"), 
                              width=unit(4, "cm"))
map

#ggsave("output/Fig4_raw.svg", height=12, width=20, dpi=2000, bg="transparent")
```


